Experimental design
===================


Profiles selection
-------------------

1. Recruitment profiles...
2. Consent profiles...
3. Profile survey...

Evaluation at CLER

1. Recruitment...
2. Consent for CLER...

Preliminary/final survey
------------------

1. Recruit survey...
2. Survey questions...

Treatment
----------

1. solicitation...
2. debriefing...


AER Registration

Power simulations
-----------------

```{r, message=FALSE, warning=FALSE, fig.width=7, fig.height=7, fig.cap="Power simulations. Relationship between simulated statistical power (y-axis) and group size (x-axis). Data are simulated from a binomial model with varying probability of success for subjects in treatment and control groups; Effect size is the difference in probability of success between control and treatment groups which is reported at the bottom of each picture; Next to each curve we have reported the corresponding probability of success in the control group. Significance computed using Chi-square test statistics with $\\alpha=0.05$. We used 20 simulations for each instance."}
# par(mfrow=c(2,2), mar=c(4.1,2.1,4.1,2.1))
# effect.size <- seq(0.01, 0.04, l=4)
# n <- seq(100, 1000, l=10)
# h <- seq(0.01, 0.10, l=10)
# 
# for (i in effect.size) {
# 	p <- simulate.power(i, num.rep=20)$power.mat
# 	plot(NA, NA, xlim=c(50, 1000), ylim=c(0, 1), type='b'
# 		, bty='n', yaxt='n', xaxt='n'
# 		, xlab=sprintf("True effect size: %0.2f",i))
# 	apply(p, 2, function(x) lines(n, x, col=2))
# 	abline(h=0.8, lty=2)
# 	axis(1, n)
# 	text(x=100, y=0.8, "Power=80%", pos=3, xpd=T)
# 	text(x=n, y=diag(p), h)
# }

```

Context
--------

We designed two interventions in collaboration with HeroX.com, a crowdsourcing platform.  We view HeroX as an example of a competitive (platform users make submissions solving a given problem and the top submissions are awarded a cash prize) and collaborative environment, respectively. 


Data
------

```{r}
# Summary stats table
```

```{r}
# Evaluation role models
```


Creating role-model profiles
-----------------

The challenge is to make realisitic role models and xxx. We recruit 19 members who have won a previous challenge: 9 men and 10 women.

We begin with bio descriptions provided by each of these members. We restrict to people with a high quality profile description that xxxx represantitive and a profile picture that can be used to xxxx (on this basis we exclude 9 profiles).

We create high quality and low quality pool of bios. The choice of names is crucial to the experiment. 
Bertrand and Mullainathan: 
 - tabulate historical names by race
 - they used survey to validate their choices

- High-low quality and Names




